The importance of measurement uncertainty in ecological management

### 2017-11-30 manuscripts/manuscript.Rmd
WIP
add drone
fix typo

This equilibrium analysis says nothig about the appropriate harvest at stock sizes above or below $B_{MSY}$, which highlights some essential differences between the optimal control policy and more typical fisheries management.  The optimal policy is impatient: it seeks to achieve the optimal yield as quickly as possible.  Below $B_{MSY}$, the economically optimal thing to do is to completely shut down the fishery, while above this stock, a harvest greater than $H_{MSY}$ can be optimal for that year.  This strategy is known as "constant escapement," since a constant sock size $B_MSY$ escapes harvest each year.  In practice, it is more common to pursue a policy of constant fishing effort (fishing mortality), $F_MSY = H_MSY / B_MSY$.  Continuing to harvest at $F_{MSY}$ when a stock is above or below $B_{MSY}$ is economically inefficient and causes depleted stocks to rebuild more slowly, but, in the absense of uncertainty, ensures a return in the long run to stock sizes of $B_MSY$ and harvests of $H_{MSY}$.  These differences will be important in understanding how these approaches perform once uncertainty is introduced.

@@

@@

@@

The year-to-year variation in quotas necessary under either a constant escapement policy
or a policy in which quotas are set by POMDP can seem impractical from a top-down
management perspective, particularly when compared to the simplicity of fixing a mortality of fishing $F_{MSY}$.
However, the economist's perspective reveals that this may not be as unrealistic as it may first appear.

Fisheries today are not managed at either their maximum ecological or economic potential.  
Taken as a whole, most ocean fisheries yield a net negative economic return
[@FAO2009], with fishing persisting only with the support of government subsidies [@Arnason2012], 
meanwhile some 68% of global fisheries are not in good biological condition [@Costello2016].
While the causes for this are both complex and numerous, we have seen that both the economic
inefficiency and ecological health are hurt by current policies, including
both MSY and it's more precautionary variants, as these all permit some level of harvest
below $B_{MSY}$.  Economists have for some time observed these inherent 
inefficiencies, and argued that the establishment of property rights in fisheries [@Arnason2012].
Approaches such as individual transferable quotas (ITQs) would incentivise
fisheries behavior to converge towards the more dynamic harvests of a constant
escapement policy, as doing so would increase the value of an individual's share.
@Arnason2012 argues that properly implemented, this would lead fisheries to desire
an even more dynamic adjustment of the TAC to maximize the value of their shares,
rather than to oppose the  @Costello2016 refers to this as Rights Based Fisheries 
Mangement, (RBFM), and it is precisely the willingness to shut down harvests for 
over-exploited fisheries that explains the faster recovery they predict under RBFM
relative to MSY. Though the @Costello2016 RBFM projections are based on a simple 
constant escapement policy which ignores uncertainty, the logic is quite general:
given property rights to establish an efficient market, it is not unrealistic to
expect fisheries adopting such dynamic polices. Indeed, the greater adoption of 
RBFM should spur the adoption of POMDP approaches as rights-holders seek strategies
that maximize the share values.  This is not to dismiss the immense practical
challenges in such an implementation, but to observe that such dynamic, better-performing
policies can be seen to embrace rather than ignore economic realities.  Notably,
the optimization approach assumed in POMDP can be easily adapted to reflect other
constraints such as the cost of idle fleets if a fishery is closed, or include
the value of ecosystem services from fish not harvested [@Halpern2013].  <!--Alternate utility functions do not increase
the complexity of the solution.  Note that fixed cost of a fleet doesn't alter the answer at all:
if you have the strategy that optimizes your profits when you have no expenses, you don't do a 
different strategy that gets less profit unless it will also lower costs.  So whether or not
you have to pay a fixed fee each year for boats, even if those boats are idle, is no reason
not to leave those boats idle.  only if leaving them idle is *more expensive* than operating them 
does this make sense, which seems unlikely.  -->

@@

@@

In 1979, a fundamental paper by William Reed [@Reed1979] proved that, under a very general assumptions, the harvest policy for a stochastically fluctuating population was identical to that of the equivalent, deterministic population.  More precisely, Reed shows that the optimal harvest of the stochastically flutuation population should always aim to reduce the population back to a constant size $S$ (termed by Reed as "escapement," while in most fisheries literature uses the term $B_{\text{MSY}$, the biomass at Maximum Sustainable Yield}).  Moreover, this value, $S$, is no more conservative than had we been able to predict future populations with perfect accuracy, as in the determinstic case of constant escapement, $D$.  A notable exception to this result is when the population is not "self-sustaining," that is,
the stochasticity is severe enough to pose an extinction risk to the unhavested population.  In such cases Reed proves there is still a single constant target population size $S$, but that $S > D$, though often by very small amount, reflecting the small probability of a purely chance extinction.

>>>>

This equilibrium analysis says nothig about the appropriate harvest at stock sizes above or below $B_{MSY}$, which highlights some essential differences between the optimal control policy and more typical fisheries management.  The optimal policy is impatient: it seeks to achieve the optimal yield as quickly as possible.  Below $B_{MSY}$, the economically optimal thing to do is to completely shut down the fishery, while above this stock, a harvest greater than $H_{MSY}$ can be optimal for that year.  This strategy is known as "constant escapement," since a constant sock size $B_{MSY}$ escapes harvest each year.  In practice, it is more common to pursue a policy of constant fishing effort (fishing mortality), $F_{MSY} = H_{MSY} / B_{MSY}$.  Continuing to harvest at $F_{MSY}$ when a stock is above or below $B_{MSY}$ is economically inefficient and causes depleted stocks to rebuild more slowly, but, in the absense of uncertainty, ensures a return in the long run to stock sizes of $B_{MSY}$ and harvests of $H_{MSY}$.  These differences will be important in understanding how these approaches perform once uncertainty is introduced.

@@

Moderate / modest sigma_g, sigma_m

@@

Is it surprising that POMDP model should do better?  Recall that Reed found stochasticity to make no difference, the deterministic model performs identically.

@@

The year-to-year variation in quotas necessary under either a constant escapement policy
or a policy in which quotas are set by POMDP can seem impractical from a top-down
management perspective, particularly when compared to the simplicity of fixing a mortality of fishing $F_{MSY}$.
However, the economist's perspective reveals that this may not be as unrealistic as it may first appear.
Fisheries today are not managed at either their maximum ecological or economic potential.  
Taken as a whole, most ocean fisheries yield a net negative economic return
[@FAO2009], with fishing persisting only with the support of government subsidies [@Arnason2012], 
meanwhile some 68% of global fisheries are not in good biological condition [@Costello2016].
While the causes for this are both complex and numerous, we have seen that both the economic
inefficiency and ecological health are hurt by current policies, including
both MSY and it's more precautionary variants, as these all permit some level of harvest
below $B_{MSY}$.  Economists have for some time observed these inherent 
inefficiencies, and argued that the establishment of property rights in fisheries [@Arnason2012].
Approaches such as individual transferable quotas (ITQs) would incentivise
fisheries behavior to converge towards the more dynamic harvests of a constant
escapement policy, as doing so would increase the value of an individual's share.
@Arnason2012 argues that properly implemented, this would lead fisheries to desire
an even more dynamic adjustment of the TAC to maximize the value of their shares,
rather than to oppose the  @Costello2016 refers to this as Rights Based Fisheries 
Mangement, (RBFM), and it is precisely the willingness to shut down harvests for 
over-exploited fisheries that explains the faster recovery they predict under RBFM
relative to MSY. Though the @Costello2016 RBFM projections are based on a simple 
constant escapement policy which ignores uncertainty, the logic is quite general:
given property rights to establish an efficient market, it is not unrealistic to
expect fisheries adopting such dynamic polices. Indeed, the greater adoption of 
RBFM should spur the adoption of POMDP approaches as rights-holders seek strategies
that maximize the share values.  This is not to dismiss the immense practical
challenges in such an implementation, but to observe that such dynamic, better-performing
policies can be seen to embrace rather than ignore economic realities.  Notably,
the optimization approach assumed in POMDP can be easily adapted to reflect other
constraints such as the cost of idle fleets if a fishery is closed, or include
the value of ecosystem services from fish not harvested [@Halpern2013].

<!--Alternate utility functions do not increase
the complexity of the solution.  Note that fixed cost of a fleet doesn't alter the answer at all:
if you have the strategy that optimizes your profits when you have no expenses, you don't do a 
different strategy that gets less profit unless it will also lower costs.  So whether or not
you have to pay a fixed fee each year for boats, even if those boats are idle, is no reason
not to leave those boats idle.  only if leaving them idle is *more expensive* than operating them 
does this make sense, which seems unlikely.  -->

@@

-----------------
<!-- MISC draft text -->

@@

In 1979, a fundamental paper by William Reed [@Reed1979] proved that, under a very general assumptions, the harvest policy for a stochastically fluctuating population was identical to that of the equivalent, deterministic population.  More precisely, Reed shows that the optimal harvest of the stochastically flutuation population should always aim to reduce the population back to a constant size $S$ (termed by Reed as "escapement," while in most fisheries literature uses the term $B_{MSY}$, the biomass at Maximum Sustainable Yield}).  Moreover, this value, $S$, is no more conservative than had we been able to predict future populations with perfect accuracy, as in the determinstic case of constant escapement, $D$.  A notable exception to this result is when the population is not "self-sustaining," that is,
the stochasticity is severe enough to pose an extinction risk to the unhavested population.  In such cases Reed proves there is still a single constant target population size $S$, but that $S > D$, though often by very small amount, reflecting the small probability of a purely chance extinction.
